\documentclass[11pt,a4paper,openright]{book}

% preamble loading
% ====================================================================
\input{Toolbox/Packages}
\input{Toolbox/Commands}
\input{Toolbox/Macros}
\input{Toolbox/Layout}
\input{Toolbox/TempPackages}

\addbibresource{bib_thesis.bib} %specify the reference .bib file

\begin{document}

	% \setcounter{minitocdepth}{3} % to change the depth of the minitoc
	\dominitoc
	\faketableofcontents

	\chapter{In-situ Thermal Control Platform for Deterministic Defect Engineering}
	\label{chap:three}
	\chaptabstract{
	Thermally induced defects in monolayer transition metal dichalcogenides (TMDs) are highly sensitive to annealing temperature, necessitating precise thermal control for deterministic defect engineering. Conventional furnace annealing requires repeated transfers between the furnace and a cryostat, with unavoidable air exposure at each step, thereby limiting reproducibility and degrading optical quality.
	
	To overcome these limitations, we developed an in-situ local heating platform fully integrated into a cryogenic micro-photoluminescence ($\mu$-PL) setup. The platform is based on a micro-heater chip consisting of a suspended SiC membrane, which undergoes Joule heating under an applied current. This design enables localized annealing up to $\sim 1200$~K while maintaining the surrounding cryostat at $\sim 3.6$~K. As a result, thermal treatment and optical characterization can be performed simultaneously under high-vacuum conditions, completely eliminating air exposure.
	
	The electrical properties of the SiC membrane are monitored in real time, providing an additional diagnostic of the heater state throughout the experiment. To accurately determine the local sample temperature, three complementary and independent thermometry approaches are employed: (i) exciton-based optical thermometry using PL and PLE spectroscopy, validated against the Pässler model over the range 3--925~K; (ii) blackbody radiation thermometry extending the calibration above 925~K; and (iii) Raman spectroscopy of the WS$_2$ $E_{2g}$ and $A_{1g}$ modes, serving as an independent temperature probe and revealing a thermal dissociation threshold near 1273~K.
	
	These methods are cross-validated and unified into a single temperature scale spanning 3--1200~K, with agreement within a few kelvin at overlapping temperature ranges. The platform further demonstrates robust mechanical stability, excellent chip-to-chip reproducibility, and a standardized annealing protocol. In particular, sub-micrometer positional stability is maintained under repeated thermal cycling, and a linear temperature--power relationship enables reliable and reproducible high-temperature control.
	}
	\minitoc
	\include{Chapters/Chapter_three}


\end{document}
